---
title: "Projetcs"
output: github_document
---
Abundance and food habits from the four pinniped’s species inhabits in Mexico. 2012-2017.

Population study and trophic ecology from the Guadalupe fur Seal, Arctocephalus townsendi. 2014-2016.

Research (population and trophic ecology) cruise over the 13 California sea lion rookeries from the Gulf of California in 2016.

Foraging ecology and population dynamic of Guadalupe fur seals from Guadalupe Island 2017 — 2020.








```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## GitHub Documents

This is an R Markdown format used for publishing markdown documents to GitHub. When you click the **Knit** button all R code chunks are run and a markdown file (.md) suitable for publishing to GitHub is generated.

## Including Code

You can include R code in the document as follows:

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
